\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section IV

In the numerical simulations reported next in Sec. \ref{sec:NumericalSimulations}, the states $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}). If one wishes so, the Euler-Maruyama scheme in Fig. \ref{fig:BlockDiagm} may be replaced by other SDE integrators, see e.g., \cite[Sec. III.B.2, Remark 1]{caluya2019TAC}.

>>>>

In the numerical simulations reported in Sec. \ref{sec:NumericalSimulations}, the states $\{\bm{x}_{k}^{i}\}_{i=1}^{N}$ are updated by the Euler-Maruyama scheme applied to (\ref{ItoSDEvectorlevel}). If one wishes so, the Euler-Maruyama scheme in Fig. \ref{fig:BlockDiagm} may be replaced by other SDE integrators, see e.g., \cite[Sec. III.B.2, Remark 1]{caluya2019TAC}.

To numerically perform the proximal updates $\{\tilde{\varrho}_{k-1}^{i}\}_{i=1}^{N}\mapsto\{\tilde{\varrho}_{k}^{i}\}_{i=1}^{N}$ for $k\in\mathbb{N}$, we implement an instance of the Algorithm 1 in \cite{caluya2019TAC}. This algorithm implements a dualization along
with an entropic regularization of the variational update \eqref{KineticProx}, and then solves the same using a fixed point
recursion that is provably contractive; see \cite[Sec. V.B]{caluya2019TAC}.
